Automatic Identification and Annotation of Tasks in Structured Programs

### 2018-04-08 docs/ACM/paper.tex
Working on scalability.

\begin{figure}[t!]
\begin{small}
\begin{eqnarray*}
\begin{tabular}{lc}
\textsc{[Instr]} &
W(\mbox{instr}) = \mbox{given by the spec.}
\\\\
\textsc{[Seq]} &
\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2}{W(S_1;S_2;) = w_2}
\\\\
\textsc{[Branch]} &
\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ W(S_3) = w_3}
{W(\mbox{if}(S_1) \ S_2; \ \mbox{else} \ S_3;) = w_1 + w_2 + w_3}
\\\\
\textsc{[LoopInf]} &
\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ \mathit{Iter}(S_1) = \infty}
{W(\mbox{while} (S_1) \ S_2;) = 10 \times (w_1 + w_2)}
\\\\
\textsc{[LoopExp]} &
\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ \mathit{Iter}(S_1) = E}
{W(\mbox{while} (S_1) \ S_2;) = E \times (w_1 + w_2)}
\end{tabular}
\end{eqnarray*}
\end{small}
\caption{\label{fig:swe}Estimating the cost of tasks.}
\end{figure}

@@

%PERFORMANCE
%Here, we show the results for our small benchmarks (toys & bots)
\subsection{Performance}.
\label{sub:performance}

@@

%OPTIMIZATIONS
%Here, we show the results on two big optimizations: recursion depth and cost model.
%We can use the same benchmarks as above.
\subsection{Optimizations}.
\label{sub:optimizations}

@@

%VERSATILITY
%The goal here is to show that TaskMiner is a versatile tool, capable of finding many types of task parallelism in the code. 
%And the types of tasks that are going to be mined can be easily set, should the programmer ever desires to.
\subsection{Versatility}.
\label{sub:versatility}

@@

%APPLICABILITY
%We'll show TaskMiner application on larger benchmarks, such as those of spec or those of the LLVM's test-suite.
\subsection{Scalability}.
\label{sub:scalability}

>>>>

\begin{figure}[t!]
\begin{small}
\begin{eqnarray*}
\begin{tabular}{lc}
\textsc{[Instr]} &
W(\mbox{instr}) = \mbox{given by the spec.}
\\\\
\textsc{[Seq]} &
\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2}{W(S_1;S_2;) = w_1 + w_2}
\\\\
\textsc{[Branch]} &
\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ W(S_3) = w_3}
{W(\mbox{if}(S_1) \ S_2; \ \mbox{else} \ S_3;) = w_1 + w_2 + w_3}
\\\\
\textsc{[LoopInf]} &
\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ \mathit{Iter}(S_1) = \infty}
{W(\mbox{while} (S_1) \ S_2;) = 10 \times (w_1 + w_2)}
\\\\
\textsc{[LoopExp]} &
\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ \mathit{Iter}(S_1) = E}
{W(\mbox{while} (S_1) \ S_2;) = E \times (w_1 + w_2)}
\end{tabular}
\end{eqnarray*}
\end{small}
\caption{\label{fig:swe}Estimating the cost of tasks.}
\end{figure}

@@

%PERFORMANCE
%Here, we show the results for our small benchmarks (toys & bots)
\subsection{Performance}
\label{sub:performance}

@@

%OPTIMIZATIONS
%Here, we show the results on two big optimizations: recursion depth and cost model.
%We can use the same benchmarks as above.
\subsection{Optimizations}
\label{sub:optimizations}

@@

%VERSATILITY
%The goal here is to show that TaskMiner is a versatile tool, capable of finding many types of task parallelism in the code. 
%And the types of tasks that are going to be mined can be easily set, should the programmer ever desires to.
\subsection{Versatility}
\label{sub:versatility}

@@

%APPLICABILITY
%We'll show TaskMiner application on larger benchmarks, such as those of spec or those of the LLVM's test-suite.
\subsection{Scalability}
\label{sub:scalability}

The analyses that we have described in Section~\ref{sec:sol} have a worst-case
quadratic time.
This is the worst-case scenario of the symbolic range analysis of
Section~\ref{sub:sra} and the task-expansion algorithm of
Section~\ref{sub:expansion}.
Nevertheless, our implementation is fast in practice.
To support this statement, we have used \textsf{CSmith}~\cite{Yang11}, a random
code generator, to produce 100 programs of varying sizes, which we then fed to
the \Taskminer.
Figure~\ref{fig:TM_Runtime} shows the result of this experiment.
Our largest program had 4,999 lines of C, and \Taskminer{} could process it
in 1.2 seconds.
the $R^2$ of polynomials of degree 1, 2, 3 and 4 is, respectively, 0.795,
0.890, 0.909 and 0.911, suggesting very small differences between polynomials
of degree 2 or more.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{images/TM_Runtime}
\caption{Runtime of \Taskminer{} vs size of input programs.
Each dot represents one of the 100 program generated by \textsf{CSmit}.
We have fit a degree-2 polynomial on this dataset.}
\label{fig:TM_Runtime}
\end{center}
\end{figure}
